Nonlinear mixed effects models for time series forecasting of smart meter demand

### 2020-10-21 paper.Rmd

Several linear and mixed effects models were tested to determine which produced the most accurate forecasts conditional on selected features. Here we describe the various benchmarking and mixed effects models and their formulations. All analysis was produced using the R statistical programming language [@R-base]. Mixed effects models were fit using the `lme4` package for mixed effects models [@R-lme4]. All code used to run this analysis has been made available in the [https://github.com/camroach87/1901-nlmets](https://github.com/camroach87/1901-nlmets) GitHub repo.

>>>>

Several linear and mixed effects models were tested to determine which produced the most accurate forecasts conditional on selected features. Here we describe the various benchmarking and mixed effects models and their formulations. All analysis was produced using the R statistical programming language [@R-base]. Mixed effects models were fit using the `lme4` package for mixed effects models [@R-lme4]. All code used to run this analysis has been made available in the [https://github.com/camroach87/1901-nlmets](https://github.com/camroach87/1901-nlmets) GitHub repository.
